---
title: "p8105_hw5_jl6648"
output: github_document
author: Jixin Li
date: "2023-11-07"
---

```{r, message=FALSE}
library(tidyverse)
library(patchwork)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "95%"
)

theme_set(theme_minimal() + theme(legend.position = 'bottom'))

options(
  ggplot2.continuous.colour = 'viridis',
  ggplot2.continuous.fill = 'viridis'
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

# problem 1


# problem 2

## Start with a dataframe containing all file names
```{r}
files_df <- tibble(
  files = list.files("data")) |>
  mutate(files = str_c("data", files, sep = "/"))
```

## Iterate over file names and read in data for each subject and tidy the result
```{r, message=FALSE}
study_df <- files_df |>
  mutate(respondents = map(files, read_csv)) |>
  mutate(arm_type = case_when(str_detect(files, "exp") ~ "experiment",
                               str_detect(files, "con") ~ "control"),
          subject_id = as.factor(parse_number(files))) |>
  unnest(respondents) |>
  pivot_longer(week_1:week_8, 
               names_to = "week", 
               values_to = "observations") |>
  mutate(week = as.numeric(parse_number(week)))
```

## Make a spaghetti plot showing observations on each subject over time
```{r}
study_df |>
  ggplot(aes(x = week, y = observations, color = subject_id)) +
  geom_line() +
  facet_grid(. ~ arm_type) +
  labs(
    title = "observations on each subject over time",
    x = "week",
    y = "observation",
  )
```

the trend of observations between control and experimental group is different. In the control group, the observation of each subject fluctuate during 8 weeks, but finally back to the observation level of week 1 and there no specific trend occur during 8 weeks. In the experimental group, there is a increase trend of observation on each subject during 8 weeks. At the end of week 8, the observation of each subject is much higher than the observation of week 1. 

# problem 3

## conduct a function and hypothesis test
```{r}
set.seed(327)

sim_normal <- function(n = 30, mu, sigma = 5){
  x = rnorm(n, mean = mu, sd = sigma)
  test <- t.test(x = x, alternative = "two.sided", conf.level = 0.95) |>
    broom::tidy() |>
    select(estimate, p.value)
}
```

## Set μ=0 and generate 5000 datasets from the model
```{r}
sim_mu_0 <- rerun(5000, sim_normal(mu = 0)) |>
  bind_rows()
```

## Repeat the above for μ={1,2,3,4,5,6}
```{r}
sim_mu = 
  tibble(
    mu = c(1, 2, 3, 4, 5, 6)
    ) |>
  mutate(outputs = map(.x = mu, ~ rerun(5000, sim_normal(30, mu = .x))),
         estimate = map(outputs, bind_rows)) |>
  unnest(estimate) |>
  select(-outputs)
```

## Make a plot showing the proportion of times the null was rejected on the y axis and the true value of μ on the x axis
```{r}
  sim_mu |>
  group_by(mu) |>
  summarize(p_value = sum(p.value < 0.05), 
            number = n(), 
            reject_prop = p_value/number) |>
  ggplot(aes(x = mu, y = reject_prop)) + 
  geom_point() + 
  geom_smooth() +
  labs(
    title = "Proportion of rejecting null hypothesis on each mu",
    x = "True Value mu", 
    y = "Proportion"
  )
```

As mu increase from 1 to 6, the proportion of rejection null hypothesis increases. There is a positive correlation between power and effect size. 

## Make a plot showing the average estimate of μ̂ on the y axis and the true value of μ on the x axis.
```{r}
sim_mu |>
  group_by(mu) |>
  summarize(ave_estimate = mean(estimate)) |>
  ggplot(aes(x = mu, y = ave_estimate)) + 
  geom_point() +
  geom_line() + 
  geom_smooth() +
  labs(
    title = "Average estimate of mu of each true value mu",
    x = "True value mu", 
    y = "Average estimate "
  )
  
```

## Make a plot showing the average estimate of μ̂ only in samples for which the null was rejected on the y axis and the true value of μ on the x axis. 
```{r}
sim_mu |>
  group_by(mu) |>
  filter(p.value < 0.05) |>
  summarize(ave_estimate = mean(estimate)) |>
  ggplot(aes(x = mu, y = ave_estimate)) + 
  geom_point() +
  geom_line() + 
  geom_smooth() +
  labs(
    title = "Average estimate of mu of each true value mu in samples of rejecting the null",
    x = "True value mu", 
    y = "Average estimate "
  )
```

according to these two plots, as the true value mu increase, the sample average of μ̂ across tests for which the null is rejected is more likely to equal to the average estimate for true value of μ. From the plots, we can tell at the mu equal to 4, 5, 6, both plots have the same average estimate; however, at the mu equal to 1, 2, 3, the average estimate for rejecting null hypothesis samples is slightly higher than the average estimate for all samples. This is because there is variability in sample estimates, and even when the null hypothesis is rejected, there can be some estimation error. 