---
title: "p8105_hw5_jl6648"
output: github_document
author: Jixin Li
date: "2023-11-07"
---

```{r, message=FALSE}
library(tidyverse)
library(patchwork)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "95%"
)

theme_set(theme_minimal() + theme(legend.position = 'bottom'))

options(
  ggplot2.continuous.colour = 'viridis',
  ggplot2.continuous.fill = 'viridis'
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

# problem 1


# problem 2

## Start with a dataframe containing all file names
```{r}
files_df <- tibble(
  files = list.files("data")) |>
  mutate(files = str_c("data", files, sep = "/"))
```

## Iterate over file names and read in data for each subject and tidy the result
```{r, message=FALSE}
study_df <- files_df |>
  mutate(respondents = map(files, read_csv)) |>
  mutate(arm_type = case_when(str_detect(files, "exp") ~ "experiment",
                               str_detect(files, "con") ~ "control"),
          subject_id = as.factor(parse_number(files))) |>
  unnest(respondents) |>
  pivot_longer(week_1:week_8, 
               names_to = "week", 
               values_to = "observations") |>
  mutate(week = as.numeric(parse_number(week)))
```

## Make a spaghetti plot showing observations on each subject over time
```{r}
study_df |>
  ggplot(aes(x = week, y = observations, color = subject_id)) +
  geom_line() +
  facet_grid(. ~ arm_type) +
  labs(
    title = "observations on each subject over time",
    x = "week",
    y = "observation",
  )
```

the trend of observations between control and experimental group is different. In the control group, the observation of each subject fluctuate during 8 weeks, but finally back to the observation level of week 1 and there no specific trend occur during 8 weeks. In the experimental group, there is a increase trend of observation on each subject during 8 weeks. At the end of week 8, the observation of each subject is much higher than the observation of week 1. 

# problem 3

## conduct a function and hypothesis test
```{r}
set.seed(1)

sim_normal = function(n = 30, mu, sigma = 5){
  x = rnorm(n, mean = mu, sd = sigma)
  test = t.test(x, mu = 0, alternative = "two.sided", conf.level = 0.95) |>
    broom::tidy() |>
    select(estimate, p.value)
}
```

## Set μ=0 and generate 5000 datasets from the model
```{r}
sim_0 = vector("list", length = 5000)

for (i in 1:5000) {
  sim_0[[i]] = sim_normal(mu = 0)
}

sim_0_results = bind_rows(sim_0)
```

## Repeat the above for μ={1,2,3,4,5,6}
```{r}
sim_mu = 
  tibble(
    mu = c(1, 2, 3, 4, 5, 6)
    ) |>
  mutate(outputs = map(mu, ~rerun(5000, sim_normal(mu=mu))),
         estimate = map(outputs, bind_rows)) |>
  unnest(estimate) |>
  select(-outputs)
```

